A Transactional Memory System for Parallel Python

### 2014-07-30 talk/dls2014/paper/paper.tex
explain why we only have micro benchs

To asses how well the STM system scales on its own (without any real
workload), we execute the loop in Listing~\ref{lst:scaling_workload}
on 1 to 4 threads on the PyPy interpreter with STM.

@@

For the results in Figure~\ref{fig:scaling}, we
normalised the average runtimes to the time it took on a single
thread. From this we see that there is additional overhead introduced
by each thread ($12.3\%$ for all 4 threads together). Every thread
adds some overhead because during a commit, there is one more thread
which has to reach a safe point. Additionally, conflict detection
needs to check for conflicts in all concurrently running transactions.

@@

For the following sections we use a set of six small benchmarks
available at~\cite{pypybenchs}:

>>>>

To asses how well the STM system in combination with a Python
interpreter scales on its own (without any real workload), we execute
the loop in Listing~\ref{lst:scaling_workload} on 1 to 4 threads on
the PyPy interpreter with STM and without a JIT.  There are very few
allocations or calculations in this loop, so the main purpose of this
benchmark is simply to check that there are no inherent conflicts in
the interpreter when everything is thread-local. We also get some
idea about how much overhead each additional thread introduces.

@@

The STM system detected no conflicts when running this code on 4
threads. For the results in Figure~\ref{fig:scaling}, we
normalised the average runtimes to the time it took on a single
thread. From this we see that there is some additional overhead introduced
by each thread ($12.3\%$ for all 4 threads together). Every thread
adds some overhead because during a commit, there is one more thread
which has to reach a safe point. Additionally, conflict detection
needs to check for conflicts in all concurrently running transactions.

@@

For the following sections we use a set of six small benchmarks
available at~\cite{pypybenchs}. There are, unsurprisingly, not
many threaded applications written in Python that can be used
as a benchmark. Since until now, threading was rarely used
for performance reasons because of the GIL, we mostly collected
small demos and wrote our own benchmarks to evaluate our system:
